|

### 2022-06-27 Luedeling_et_al_2022_supplementary_materials.Rmd
new html doc - supplement

one_slice<-ggplot(data=data.frame(CO2eq_per_milk=slice_2000$resampled), aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~at~2000~kg~milk~per~head~(kg~CO[2]*'-eq'~kg^-1))) + theme_bw() + ggtitle("a) Slice through the emission intensity distribution")

@@

two_slices<-ggplot(data=slices, aes(Values, fill=Level)) +
 geom_density(alpha=.2) +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~at~specific~milk~yield~per~head~(kg~CO[2]*'-eq'~kg^-1))) + labs(fill='Productivity level') + theme_bw() + ggtitle("b) Two slices at different productivity levels")

@@

```{r, fig.dim = c(4, 6), warning=FALSE, message=FALSE, fig.cap="***Figure 9.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emission intensity changes have actually occurred. Type I errors indicate the probability of failing to recognize households that implemented interventions, whereas the Type II error represents the percentage of households that did not make any changes, but are nevertheless rewarded due to random effects.*"}

@@

for(i in 1:nrow(confidence_level_analysis))
{# compute Type 1 errors for all interventions
  for(ints in c("breed", "nobull", "lessReplace", "Calliandra", "balance"))
    confidence_level_analysis[i,ints]<-
      length(which(int_none_plot$intervention==ints &
                     int_none_plot$confidence_level <
                     confidence_level_analysis$confidence[i])) /
      length(which(int_none_plot$intervention==ints)) * 100

  confidence_level_analysis$Type2error[i]<-
    length(which(int_none_plot$intervention=="none" &
                   int_none_plot$confidence_level>confidence_level_analysis$confidence[i])) /
    length(which(int_none_plot$intervention=="none")) * 100

@@

confidence_level_analysis$confidence<-confidence_level_analysis$confidence*100
confidence_plot<-melt(confidence_level_analysis,id.vars = "confidence")
confidence_plot$variable <- factor(confidence_plot$variable, levels = c("breed", "nobull", "lessReplace", "Calliandra", "balance", "Type2error"),
                  labels = c("Type I error - failure to reward 'Breed change' adopters",
                             "Type I error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type I error - failure to reward 'Fewer replacement males' adopters",
                             "Type I error - failure to reward 'Calliandra feed' adopters",
                             "Type I error - failure to reward 'Balanced diet' adopters",
                             "Type II error - rewarding non-adopters"))

@@

```{r, fig.dim = c(8, 12), fig.cap="***Figure S12.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emission intensity changes have actually occurred, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). Type I errors indicate the probability of failing to recognize households that implemented interventions, whereas the Type II error represents the percentage of households that did not make any changes, but are nevertheless rewarded due to random effects.*"}

@@

for(i in 1:nrow(confidence_level_analysis_update))
{# compute Type 1 errors for all interventions
  for(ints in c("breed", "nobull", "lessReplace", "Calliandra", "balance"))
    confidence_level_analysis_update[i,ints]<-
      length(which(int_none_plot_update$intervention==ints &
                     int_none_plot_update$confidence_level <
                     confidence_level_analysis_update$confidence[i])) /
      length(which(int_none_plot_update$intervention==ints)) * 100

  confidence_level_analysis_update$Type2error[i]<-
    length(which(int_none_plot_update$intervention=="none" &
                   int_none_plot_update$confidence_level>confidence_level_analysis_update$confidence[i])) /
    length(which(int_none_plot_update$intervention=="none")) * 100

@@

confidence_level_analysis_update$confidence<-confidence_level_analysis_update$confidence*100
confidence_plot_update<-melt(confidence_level_analysis_update,id.vars = "confidence")
confidence_plot_update$variable <- factor(confidence_plot_update$variable, levels = c("breed", "nobull", "lessReplace", "Calliandra", "balance", "Type2error"),
                  labels = c("Type I error - failure to reward 'Breed change' adopters",
                             "Type I error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type I error - failure to reward 'Fewer replacement males' adopters",
                             "Type I error - failure to reward 'Calliandra feed' adopters",
                             "Type I error - failure to reward 'Balanced diet' adopters",
                             "Type II error - rewarding non-adopters"))

confidence_plot_update[,"version"]<-"Precise milk yields"
confidence_plot[,"version"]<-"Initial uncertainty"
confidence_plot_stuff<-rbind(confidence_plot,confidence_plot_update)
confidence_plot_stuff$variable <- factor(confidence_plot_stuff$variable,
                                         levels = c("Type I error - failure to reward 'Breed change' adopters",
                             "Type I error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type I error - failure to reward 'Fewer replacement males' adopters",
                             "Type I error - failure to reward 'Calliandra feed' adopters",
                             "Type I error - failure to reward 'Balanced diet' adopters",
                             "Type II error - rewarding non-adopters"),
                  labels = c("Type I - 'Breed change'",
                             "Type I - 'Unproductive bulls'",
                             "Type I - 'Replacement males'",
                             "Type I - 'Calliandra feed'",
                             "Type I - 'Balanced diet'",
                             "Type II"))

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure 11.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emission intensity changes have actually occurred, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). Type I errors indicate the probability of failing to recognize households that implemented interventions, whereas the Type II error represents the percentage of households that did not make any changes, but are nevertheless rewarded due to random effects.*"}

ggplot(confidence_plot_stuff, aes(x=confidence,y=value, color=variable)) + geom_smooth(stat="identity", fill="darkolivegreen") +
  labs(y="Error probability (%)", x="Required confidence that emission reductions have occurred (%)",
       color="Classification errors") +
  facet_wrap(~version,nrow=2) +
  scale_color_manual(values= c("Type I - 'Breed change'" = intervention_colors[1],
                              "Type I - 'Unproductive bulls'" = intervention_colors[2],
                              "Type I - 'Replacement males'" = intervention_colors[3],
                              "Type I - 'Calliandra feed'" = intervention_colors[4],
                              "Type I - 'Balanced diet'" = intervention_colors[6],
                              "Type II" = "blue"),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet", "Type II error")) + theme_bw()

>>>>

one_slice<-ggplot(data=data.frame(CO2eq_per_milk=slice_2000$resampled), aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.5, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~at~2000~kg~milk~per~head~(kg~CO[2]*'-eq'~kg^-1))) + theme_bw() + ggtitle("a) Slice through the emission intensity distribution")

@@

two_slices<-ggplot(data=slices, aes(Values, fill=Level)) +
 geom_density(alpha=.5) +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~at~specific~milk~yield~per~head~(kg~CO[2]*'-eq'~kg^-1))) + labs(fill='Productivity level') + theme_bw() + ggtitle("b) Two slices at different productivity levels")

@@

```{r, fig.dim = c(4, 6), warning=FALSE, message=FALSE, fig.cap="***Figure 9.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emission intensity changes have actually occurred. Type I errors indicate the probability of recognizing households for reducing emissions, even though they did not adopt an innovation, whereas the Type II error represents the percentage of households that made changes, but are not recognized for these.*"}

@@

for(i in 1:nrow(confidence_level_analysis))
{# compute Type 2 errors for all interventions
  for(ints in c("breed", "nobull", "lessReplace", "Calliandra", "balance"))
    confidence_level_analysis[i,ints]<-
      length(which(int_none_plot$intervention==ints &
                     int_none_plot$confidence_level <
                     confidence_level_analysis$confidence[i])) /
      length(which(int_none_plot$intervention==ints)) * 100

  confidence_level_analysis$Type1error[i]<-
    length(which(int_none_plot$intervention=="none" &
                   int_none_plot$confidence_level>confidence_level_analysis$confidence[i])) /
    length(which(int_none_plot$intervention=="none")) * 100

@@

confidence_level_analysis$confidence<-confidence_level_analysis$confidence*100
confidence_plot<-melt(confidence_level_analysis,id.vars = "confidence")
confidence_plot$variable <- factor(confidence_plot$variable, levels = c("breed", "nobull", "lessReplace", "Calliandra", "balance", "Type1error"),
                  labels = c("Type II error - failure to reward 'Breed change' adopters",
                             "Type II error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type II error - failure to reward 'Fewer replacement males' adopters",
                             "Type II error - failure to reward 'Calliandra feed' adopters",
                             "Type II error - failure to reward 'Balanced diet' adopters",
                             "Type I error - rewarding non-adopters"))

@@

```{r, fig.dim = c(8, 12), fig.cap="***Figure S12.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emission intensity changes have actually occurred, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). Type I errors indicate the probability of recognizing households for reducing emissions, even though they did not adopt an innovation, whereas the Type II error represents the percentage of households that made changes, but are not recognized for these.*"}

@@

for(i in 1:nrow(confidence_level_analysis_update))
{# compute Type 2 errors for all interventions
  for(ints in c("breed", "nobull", "lessReplace", "Calliandra", "balance"))
    confidence_level_analysis_update[i,ints]<-
      length(which(int_none_plot_update$intervention==ints &
                     int_none_plot_update$confidence_level <
                     confidence_level_analysis_update$confidence[i])) /
      length(which(int_none_plot_update$intervention==ints)) * 100

  confidence_level_analysis_update$Type1error[i]<-
    length(which(int_none_plot_update$intervention=="none" &
                   int_none_plot_update$confidence_level>confidence_level_analysis_update$confidence[i])) /
    length(which(int_none_plot_update$intervention=="none")) * 100

@@

confidence_level_analysis_update$confidence<-confidence_level_analysis_update$confidence*100
confidence_plot_update<-melt(confidence_level_analysis_update,id.vars = "confidence")
confidence_plot_update$variable <- factor(confidence_plot_update$variable, levels = c("breed", "nobull", "lessReplace", "Calliandra", "balance", "Type1error"),
                  labels = c("Type II error - failure to reward 'Breed change' adopters",
                             "Type II error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type II error - failure to reward 'Fewer replacement males' adopters",
                             "Type II error - failure to reward 'Calliandra feed' adopters",
                             "Type II error - failure to reward 'Balanced diet' adopters",
                             "Type I error - rewarding non-adopters"))

confidence_plot_update[,"version"]<-"Precise milk yields"
confidence_plot[,"version"]<-"Initial uncertainty"
confidence_plot_stuff<-rbind(confidence_plot,confidence_plot_update)
confidence_plot_stuff$variable <- factor(confidence_plot_stuff$variable,
                                         levels = c("Type II error - failure to reward 'Breed change' adopters",
                             "Type II error - failure to reward 'Retire unproductive bulls' adopters",
                             "Type II error - failure to reward 'Fewer replacement males' adopters",
                             "Type II error - failure to reward 'Calliandra feed' adopters",
                             "Type II error - failure to reward 'Balanced diet' adopters",
                             "Type I error - rewarding non-adopters"),
                  labels = c("Type II - 'Breed change'",
                             "Type II - 'Unproductive bulls'",
                             "Type II - 'Replacement males'",
                             "Type II - 'Calliandra feed'",
                             "Type II - 'Balanced diet'",
                             "Type I"))

@@

```{r, fig.dim = c(8, 8), fig.cap="***Figure 11.*** *Probability of Type I and Type II errors incurred by choosing specific levels of confidence that emission intensity changes have actually occurred, comparing initial uncertainty with improved measurements of milk yields (assuming a reduction of measurement errors to 15%). Type I errors indicate the probability of recognizing households for reducing emissions, even though they did not adopt an innovation, whereas the Type II error represents the percentage of households that made changes, but are not recognized for these.*"}

ggplot(confidence_plot_stuff, aes(x=confidence,y=value, color=variable)) + geom_smooth(stat="identity", fill="darkolivegreen") +
  labs(y="Error probability (%)", x="Required confidence that emission reductions have occurred (%)",
       color="Classification errors") +
  facet_wrap(~version,nrow=2) +
  scale_color_manual(values= c("Type II - 'Breed change'" = intervention_colors[1],
                              "Type II - 'Unproductive bulls'" = intervention_colors[2],
                              "Type II - 'Replacement males'" = intervention_colors[3],
                              "Type II - 'Calliandra feed'" = intervention_colors[4],
                              "Type II - 'Balanced diet'" = intervention_colors[6],
                              "Type I" = "blue"),
                    labels = c("Breed change", "No bulls", "Fewer males", "Calliandra feed", "Balanced diet", "Type I error")) + theme_bw()
